---
title: "Final Project"
author: "Tanya Chen, Allison Bleicher"
format: pdf:
    geometry: 
      - left=1in
      - right=1in
      - top=1in
      - bottom=1in
---

## Introduction

## Exploratory Analysis

## Result

To investigate whether the initial total price (the sum of starting price and shipping price) equals to the dealing price, we need to conduct a two sample mean T test. In words, the null hypothesis for the hypothesis testing is that there is no difference between the initial total price and the dealing price.  The alternative hypothesis is that there is a difference between the initial total price and the dealing price of Mario Kart. In symbols: 
$$H_0: \mu_{diff} = 0$$ 
$$H_A: \mu_{diff} \ne 0$$

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
suppressWarnings({
  library(tidyverse)
  library(openintro)
})

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Read dataset
# if you want to read the document in your 
marioKart <- read_csv('/Users/tanyachen/Documents/sds220/Final Project/mariokart.csv')

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the total price based on initial starting and shipping price
initial_total_pr <- marioKart$start_pr + marioKart$ship_pr

# Summarize the initial total price and final total price into a table


# Calculate the difference between initial total price and final total price and add it into the dataframe

```

The type of test being used is clear.
Assumptions are investigated.
The hypothesis test has a clear connection to the research question.
The test statistic, p-value, degrees of freedom, confidence interval, and significance level are explained/provided. (Only some of these will be applicable for each project)
For confidence intervals: corresponding interpretations are provided.
For linear regression models: coefficients are interpreted.
Explain any statistics or figures used for the hypothesis test.
Results are interpreted correctly and in context. 

## Discussion