---
title: "Final Project"
author: "Tanya Chen, Allison Bleicher"
format: 
  pdf:
    geometry: 
      - left=1in
      - right=1in
      - top=1in
      - bottom=1in
---

## Introduction

## Exploratory Analysis

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Load packages
suppressWarnings({
  library(tidyverse)
  library(openintro)
  library(googlesheets4)
  
})

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Importing dataset
# Read the document from google spreadsheet Mario Kart
marioKart <- read_sheet('https://docs.google.com/spreadsheets/d/1jhiTFaaJ4ZCUA9yMNFGQ2xnKItXewaNmzu6y0Syw_dk/edit?gid=1751719576#gid=1751719576')

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the total price based on initial starting and shipping price
initial_total_pr <- marioKart$start_pr + marioKart$ship_pr

dealing_pr <- marioKart$total_pr

# Summarize the initial total price and final total price into a table
price_Table <- data_frame(initial_total_pr, dealing_pr)
glimpse(price_Table)

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the difference between initial total price and final total price and add it into the dataframe
price_Difference <- marioKart$total_pr - initial_total_pr

price_Table <- data_frame(initial_total_pr, dealing_pr, price_Difference)

```

## Result

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Grading Rule Breaks for Results

# The type of test being used is clear.
# Assumptions are investigated.
# The hypothesis test has a clear connection to the research question.
# The test statistic, p-value, degrees of freedom, confidence interval, and significance level are explained/provided. (Only some of these will be applicable for each project)
# For confidence intervals: corresponding interpretations are provided.
# For linear regression models: coefficients are interpreted.
# Explain any statistics or figures used for the hypothesis test.
# Results are interpreted correctly and in context. 

```


To investigate whether the average initial total price (the sum of starting price and shipping price) equals to the average dealing price, we need to conduct a two sample mean T test. 

#### Hypotheses
Before starting hypothesis testing, we need to bring out null hypothesis and alternative hypothesis of our research question. Our null hypothesis for the hypothesis testing is that there is no difference between the mean initial total price and the mean dealing price. Our alternative hypothesis is that there is a difference between the mean initial total price and the mean dealing price of Mario Kart. In symbols: 
$$H_0: \mu_{diff} = 0$$ 
$$H_A: \mu_{diff} \ne 0$$
To investigate whether our null hypothesis is true, we need to conduct a **T Test for paired means**. 

#### Checking Conditions
Before conducting the hypothesis testing, we need to check the conditions: **independence** and **normality**. 

##### Independence
Independence checks whether the data within the groups are independent. Since the `mariokart` dataset is collected, it is a simple random sample, and we can assume that each pair of the initial total price and the dealing price are independent. 

##### Normality
Normality checks whether the difference of the paired data is roughly symmetric without large outliers.
```{r,echo = FALSE, message = FALSE, warning = FALSE}
price_Table|>
  ggplot(aes(x = price_Difference)) +
  geom_boxplot() +
  theme_bw()
  
```
Based on the boxplot above, the distribution of the difference of initial total price and dealing price are roughly normal with three outliers. There is an outlier that significantly differs from the distribution.

#### Calculation
Using t test for paired means, we will compute T-Statistics, degrees of freedom, p-value, and confidence interval with a significance level $\alpha = 0.05$.

##### R Code Overview
In RStudio, we can use `t.test(initial_total_pr,dealing_pr, paired = TRUE, alternative = "two.sided")` to calculate t statistics, degrees of freedom, p-value, and confidence interval of the difference between the initial and dealing price of Mario Kart game on EBay:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate test statistics using RStudio
t_test_pr_diff <-t.test(initial_total_pr,dealing_pr, paired = TRUE, alternative = "two.sided")
t_test_pr_diff
```

Aside from R code, we also can compute T-statistics, degrees of freedom, p-value, and confidence interval based on their mathematical formulas.

##### T-Statistics
T statistics means the ratio of how the sample mean difference varies from zero as compared to how the observations vary. We compute T statistics using the formula below:
$$T = \frac{\bar{x}_{paired}}{\sqrt{\frac{S^2_{paired}}{n}}}$$
```{r, echo = FALSE, message = FALSE, warning = FALSE}
x_bar_paired <- mean(initial_total_pr) - mean(dealing_pr)
s_paired <- sd(price_Difference)
n <- 143
t_statistics <- x_bar_paired/sqrt(s_paired*s_paired/n)
summary_table <- data_frame(n, x_bar_paired, s_paired, t_statistics)
summary_table

```
Since $n = 143$, $\bar{x}_{paired} = -37.9596$, and $S_{paired} = 27.4549$, the T-statistics equals to:
$$T = \frac{\bar{x}_{paired}}{\sqrt{\frac{S^2_{paired}}{n}}} = \frac{-37.9596}{\sqrt{\frac{27.4549^2}{143}}} = -16.534$$
##### Degrees of Freedom
The degrees of freedom, meaning that, equals to $df = n-1 = 143-1 = 142$
```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Calculate the degrees of freedom
df <- 143-1
```

##### P-Value
After calculating the t statistics and degrees of freedom, we can calculate p-value using R code `2*pt(t_statistics,df,lower.tail = TRUE)`. Since our alternative hypothesis is $H_A: \mu_{diff} \ne 0$, our p-value is two-tailed.
```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This code chunk will include calculation of p-value
# Defining the significance level
# Calculate p-value
# Create a histogram
# Explaining the p-value
# Provide a conclusion
p_value <- 2*pt(t_statistics, df, lower.tail = TRUE)

```
Based on R code, the p-value equals to $6.584 *10^{-35}$. Since our p-value is very small and approximately equals to zero, our p-value is smaller than the significance level $\alpha = 0.05$. Therefore, there is a strong evidence to reject the null hypothesis that there is no difference between the mean initial total price and the mean dealing price of Mario Kart in EBay.

##### Confidence Interval
Confidence interval is 
```{r, echo = FALSE, message = FALSE, warning = FALSE}
# This code chunk will include calculation of confidence interval
# Defining and explaining confidence interval
# Providing mathematical formula for calculating confidence interval
# Calculate confidence interval
# Explain confidence interval and provide a conclusion

```

## Discussion

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Grading Rubric for discussion

# A summary of your overall findings are explained in a clear and straightforward manner such that a person without statistical training or domain expertise can understand them.
# Results are tied back to the research question.
# Limitations of the analysis/data are acknowledged.
# It is explained/assessed if the sample is representative of your population of interest. (Hint: Most samples have some limitations. It is okay to have a sample that is not perfect, but you must be able to identify why the sample may not represent the population.)
# Discussion of future directions or extensions to this project you want to consider.

```


